Language learning via recursive pragmatic reasoning

### 2013-05-31 praglearn.tex
remove stray bit of detritus
remove repeated line in table

\begin{table}[t]
\label{tab:results}
\begin{center}
\begin{tabular}{lccccc}
\toprule
Phenomenon & Ref. & WL & PI & PI+U & PI+WL \\
\midrule
Interpreting specificity implicature & \cite{grice1975} &  & x &x & x\\
Interpreting Horn implicature & \cite{horn1984} & &  & x& x\\
Cross-situational learning & \cite{smith2008} & x& & & x \\
Disambiguating new words using old words & \cite{markman1988} &x  & & & x \\
Disambiguation without mapping & \cite{horst2008} &  & & & x \\
Learning/lexicalization of specificity implicature & \cite{levinson2000} & & & & x \\
Emergence of novel \& efficient communicative systems & \cite{galantucci2005} & & & & x \\
Lexicalization of Horn implicature & \cite{horn1984} & & & & x \\
Non-lexicalization of specificity implicature & \cite{levinson2000} & & & & x \\
\hline
\end{tabular}
\end{center}
\caption{Empirical results and references. WL refers to the word
  learning model of \cite{frank2009}; PI refers to the recursive
  pragmatic inference model of \cite{frank2012}; PI+U refers to the
  pragmatic inference model of \cite{bergen2012} which includes
  lexical uncertainty, marginalizes it out, and then recurses. Our
  current model is referred to here as PI+WL, and combines pragmatic
  inference with word learning.}
\end{table}

@@

agents not sure whether some literally means some-not-all or not,
could lexicalize given the right kind of input, but regular pragmatic
strengthening alone is not enough

>>>>

\begin{table}[t]
\label{tab:results}
\begin{center}
\begin{tabular}{lccccc}
\toprule
Phenomenon & Ref. & WL & PI & PI+U & PI+WL \\
\midrule
Interpreting specificity implicature & \cite{grice1975} &  & x &x & x\\
Interpreting Horn implicature & \cite{horn1984} & &  & x& x\\
Cross-situational learning & \cite{smith2008} & x& & & x \\
Disambiguating new words using old words & \cite{markman1988} &x  & & & x \\
Disambiguation without mapping & \cite{horst2008} &  & & & x \\
Emergence of novel \& efficient communicative systems & \cite{galantucci2005} & & & & x \\
Lexicalization of Horn implicature & \cite{horn1984} & & & & x \\
Non-lexicalization of specificity implicature & \cite{levinson2000} & & & & x \\
\hline
\end{tabular}
\end{center}
\caption{Empirical results and references. WL refers to the word
  learning model of \cite{frank2009}; PI refers to the recursive
  pragmatic inference model of \cite{frank2012}; PI+U refers to the
  pragmatic inference model of \cite{bergen2012} which includes
  lexical uncertainty, marginalizes it out, and then recurses. Our
  current model is referred to here as PI+WL, and combines pragmatic
  inference with word learning.}
\end{table}

@@

% agents not sure whether some literally means some-not-all or not,
% could lexicalize given the right kind of input, but regular pragmatic
% strengthening alone is not enough
